Convex Surrogates via Polyhedral Losses

### 2019-02-02 cvx-fin.tex
Tinkering with Theorem 28

  \raft{I might be delusional, but this second part ended up being much slicker than I'd thought, by essentially chaining definitions and maps.  Please check!}
  For the second part, let $\gamma':\simplex\toto\R'$ be the finite elicitable property embedded by $L$, with embedding $\varphi:\R'\to\reals^d$, and let $\psi$ be a calibrated link $\psi$ to a non-redundant elicitable property $\gamma:\simplex\toto\R$.
  Then letting $\psi' = (\psi \circ \varphi):\R'\to\R$, we see that $\psi'$ is a calibrated link from $\gamma'$ to $\gamma$:
  for all $r'\in\R'$, we have $\gamma'_{r'} = \prop{L}_{\varphi(r')} \subseteq \gamma_{\psi(\varphi(r'))}$.
  In particular, $\gamma'$ refines $\gamma$, and as $\gamma'$ is finite, $\gamma$ must be finite.
\end{proof}

@@

WLOG, suppose $v_1 = (0,1)$ and they are numbered clockwise with $\|v_1\| \geq \|v_j\| (\forall j \neq i)$.
Let $\theta_{i,j}$ be the clockwise angle between $v_i$ and $v_j$.
The vectors point to the sides of an irregular pentagon $T^* = \{w : Vw \leq \vec{1}\}$.
Let $w_{1,2}$ be the corner of this pentagon between $v_1$ and $v_2$, and so on.
In our case, each $S_y$ is the intersection of $T^*$ with a halfspace, $T_y = \{w \in T^* : \inprod{v_y}{w} \leq -1\}$.
So in particular, $(V,B_1)$ is tight only if all three vertices $w_{23},w_{34},w_{45}$ satisfy $\inprod{v_1}{w} \leq -1$.
(If for example $\inprod{v_1}{w_{23}} > -1$, then the constraint $\inprod{v_2}{w} \leq 1$ is not tight, i.e. there is a separation between it and $T_1$.)
Because $v_1$ is the largest vector by assumption, this implies $\theta_{13} \geq 180^{\circ}$, but it also implies $\theta_{41} \geq 180^{\circ}$, which is a contradiction (both vectors would have to lie directly opposite $v_1$, but then they would be equal).
\end{proof}

@@

\begin{theorem}
  Abstain with $\alpha > 1/2$ and $|\Y|=7$ is not $2$-embeddable.
\end{theorem}
\begin{proof}
  Like Theorem~\ref{thm:abs-5outcome-not-2embed}, we will again look at the abstain cell.  
  First, note that when $\alpha \geq \frac{n-1}{n}$, the abstain property decomposes into the mode, as the abstain cell is empty, so we can restrict to $\frac{n-1}{n} > \alpha > 1/2$.
  We then write the matrix $B$ describing the abstain cell as follows:
	\[ B = \begin{pmatrix}
       -\beta &  1 &  1 & \cdots & 1  \\
       1  & -\beta &  1 & \cdots & 1  \\
          &    &    & \vdots &    \\
       1  &  1 &  1 & \cdots & -\beta
     \end{pmatrix} .
  \]

  We know that $\beta := 1 - \frac{1}{\alpha} \in (0,1)$ as the inequalities are strict.
  Consider two requirements of the polytope: first, for all $i \in \{1,2, \ldots, 6\}, ||v_i|| > 0$.
  Additionally, we know $-\beta < 0$.
  Therefore, there will always be some $T_i$ such that $0 \not \in T_i$.
  Specifically, if, as before, we say $||v_1|| \geq ||v_j||$ for all $j \neq 1$, we know that $0 \not \in T_1$.

  By a similar argument to Theorem~\ref{thm:abs-5outcome-not-2embed}, we then must observe $\theta_{j, j+3} > 180^o$ in order to have some $w$ that satisfies our tightness constraint for $j+3$.
  That is, the existence of an $x \in S_i$ such that $\inprod{v_{j+3}}{x} = 1 \implies \theta_{j,j+3} > 180^o$.
  However, this implies $\theta_{j+3, j} < 180^o$, and therefore, there is no $x$ such that $\inprod{v_j}{x} = 1$.

  Like the triangle observed in the previous proof, we observe that $T_1$ is a trapezoid with some constraints that are not tight.
\end{proof}

>>>>

  \raft{I might be delusional, but this second part ended up being much slicker than I'd thought, by essentially chaining definitions and maps.  Please check!}
  For the second part, let $\gamma':\simplex\toto\R'$ be the finite elicitable property embedded by $L$, with embedding $\varphi:\R'\to\reals^d$, and let $\psi$ be a calibrated link to a non-redundant elicitable property $\gamma:\simplex\toto\R$.
  Then letting $\psi' = (\psi \circ \varphi):\R'\to\R$, we see that $\psi'$ is a calibrated link from $\gamma'$ to $\gamma$:
  for all $r'\in\R'$, we have $\gamma'_{r'} = \prop{L}_{\varphi(r')} \subseteq \gamma_{\psi(\varphi(r'))}$.
  In particular, $\gamma'$ refines $\gamma$, and as $\gamma'$ is finite, $\gamma$ must be finite.
\end{proof}

@@

WLOG, suppose $v_1 = (0,1)$ and they are numbered clockwise with $\|v_1\| \geq \|v_j\| (\forall j \neq i)$.
Let $\theta_{i,j}$ be the clockwise angle between $v_i$ and $v_j$.
The vectors point to the sides of an irregular pentagon $T^* = \{w : Vw \leq \vec{1}\}$.
Let $w_{1,2}$ be the corner of this pentagon between $v_1$ and $v_2$, and so on.
In our case, each $T_y$ is the intersection of $T^*$ with a halfspace, $T_y = \{w \in T^* : \inprod{v_y}{w} \leq -1\}$.
So in particular, $(V,B_1)$ is tight only if all three vertices $w_{23},w_{34},w_{45}$ satisfy $\inprod{v_1}{w} \leq -1$.
(If for example $\inprod{v_1}{w_{23}} > -1$, then the constraint $\inprod{v_2}{w} \leq 1$ is not tight, i.e. there is a separation between it and $T_1$.)
Because $v_1$ is the largest vector by assumption, this implies $\theta_{13} \geq 180^{\circ}$, but it also implies $\theta_{41} \geq 180^{\circ}$, which is a contradiction (both vectors would have to lie directly opposite $v_1$, but then they would be equal).
\end{proof}

@@

\begin{theorem}
  Abstain with $\alpha > 1/2$ and $|\Y|=7$ is not $2$-embeddable.
\end{theorem}
\begin{proof}
  Like Theorem~\ref{thm:abs-5outcome-not-2embed}, we will again show that there is no $2$-construction of the abstain cell.  
  First, note that when $\alpha \geq \frac{n-1}{n}$, the abstain property decomposes into the mode, as the abstain cell is empty, so we restrict to $\frac{n-1}{n} > \alpha > 1/2$.
  We then write the matrix $B$ describing the abstain cell as follows:
	\[ B = \begin{pmatrix}
       -\beta &  1 &  1 & \cdots & 1  \\
       1  & -\beta &  1 & \cdots & 1  \\
          &    &    & \vdots &    \\
       1  &  1 &  1 & \cdots & -\beta
     \end{pmatrix} .
  \]

  We know that $\beta := 1 - \frac{1}{\alpha} \in (0,1)$ as the inequalities describing $\alpha$ are strict.
  Observe that for all $i \in \{1,2, \ldots, 6\}, ||v_i|| > 0$.
  Additionally, we know $-\beta < 0$.
  Therefore, for all $i$, we know that $0 \not \in T_i$.
  By convexity of $T_i$ for all $i$, we then know that there is no line containing the origin in $T_i$.
  WLOG, as before, we say $v_1 = (0,1)$ and $||v_1|| \geq ||v_j||$ for all $j \neq 1$, we know that $\vec{0} \not \in T_1$.

  We assert that, in order for $(V, T_1)$ to be tight, then for all $j \neq i$, there must be a $w \in T_1$ such that $\inprod{v_j}{w} = 1$.
  However, in order for that to be true, $\theta_{1,j} > 60^o$. for all $j \neq 1$.
  Namely, $\theta_{1,2} > 60^o$, and $\theta_{6,1} > 60^o$.
  Observe that this argument is similar to the argument of Theorem~\ref{thm:abs-5outcome-not-2embed}.

  Applying the same argument iteratively, we know that if $v_c$ is the second-longest normal, in order for $(V, T_c)$ to be tight, we must observe $\theta_{j-1, j} > 60^o$ and $\theta_{j,j+1} > 60^o$.
  In fact, this argument must hold for each $\theta_j, j+1$.
  Additionally, we see for all $j$, that $\theta_{j,j+2} > 120^o$.
  However, since we know $\sum_{i=1}^6 \theta_{i,i+2} = 720$, and thus there must be some $\theta_{i,i+2} \leq 120$, yielding a contradiction.

  For the normals $v_i$ and $v_{i+2}$ such that $\theta_{i,i+2} \leq 120^o$, there is no way for the H-representation $(V, T_{i+1})$ to be tight. \jessie{.....}

  Therefore, there is no $V$ yielding a $2$-construction for abstain and $\alpha > 1/2$.

  Like the triangle observed in the previous proof, we observe that, on the regular hexagon, $T_1$ is a trapezoid with some constraints that are not tight.
\end{proof}
